---
title: "Potential changes of macrophyte species richness"
author: "Anne Lewerentz, Markus Hoffmann, Juliano S. Cabral et al"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: true
    toc: true
    toc_float: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message=FALSE, out.width = "80%")
```


# Methods and Setup 
## Load Packages 
```{r load packages, results='hide', message=FALSE}
library(LewerentzEtAl2022)
library(data.table)
library(here)
library(tidyverse)
library(styler)
library(corrplot)
library(RColorBrewer)
library(ggrepel)
library(ggpmisc)
library(ggpubr)
library(kableExtra)
library(knitr)
library(BBmisc) #normalize function
library(factoextra) #PCA
library(magrittr)

# GLM outputs
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(jtools)
library(patchwork) # combine figures
library(colorBlindness) # check colors
library(rcartocolor)

```



## Set theme & colors
```{r create ggplot theme, fig.height=2.5}

theme_analysis <- function(base_size = 14) {
  theme_minimal(base_size = base_size) %+replace%
    theme(
      # changed theme options
    )
}
# Changing the default theme
theme_set(theme_analysis())


# SET COLOR SCHEMES
scale_colour_continuous <- scale_colour_viridis_c
scale_colour_discrete   <- scale_colour_viridis_d
scale_colour_binned     <- scale_colour_viridis_b

# See options within package
#display_carto_all(colorblind_friendly = TRUE)

depthPalette <- carto_pal(5, "Teal")[2:5]
TempPalette<- carto_pal(3, "Peach")
TurbNutrPalette<- carto_pal(7, "Earth")[c(1:4)]
WinnerLoserPalette<- c(carto_pal(2,"PinkYl")[c(2)],carto_pal(2,"TealGrn")[c(1)])
#TrophiePalette <- c(carto_pal(4, "BrwnYl"))[-1] #oligo, meso, eu, others
TrophiePalette <- c("cornflowerblue","aquamarine4","coral4")
#displayAllColors(TrophiePalette)

#displayAllColors(depthPalette) + 
  #displayAllColors(TempPalette) + 
  #displayAllColors(TurbNutrPalette) +
  #displayAllColors(WinnerLoserPalette)+
  displayAllColors(TrophiePalette)
```


```{r}
# SPlength <- length(Makroph_commLastYear)-3
# Makroph_commLastYear$GAMMA <- vegan::specnumber(Makroph_commLastYear[,c(4:85)])
# 
# Makroph_commLastYearfin<-Makroph_commLastYear %>% # %>%
#   filter(!Lake %in% c("Altmuehlsee", "Drachensee", "Eixendorfer See",
#                      "Grosser Brombachsee",
#                      "Gruentensee","Igelsbachsee", 
#                      "Kleiner Brombachsee",
#                      "Liebensteinspeicher","Rottachsee", 
#                      "Steinberger See","Untreusee",
#                      "Walchensee","Murnersee","Rothsee",
#                      "Seehamer See"))%>%
#   select(where(~ any(. != 0)))
# 
# MAK_MAPPED_NSPEC <- Makroph_commLastYearfin %>%
#   select(-Lake, -YEAR, -Depth, -GAMMA) %>% ncol()
# 
# MAK_MAPPED<-Makroph_commLastYearfin %>% 
#   #rename(Lake=Gewässer, Depth=Tiefe) %>% #%>%  spread(Depth, GAMMA)
#   select(Lake, YEAR, Depth, GAMMA) %>%
#   mutate(GAMMAperc = GAMMA/MAK_MAPPED_NSPEC*100)
# 
# MAK_MAPPED$LakeID <- MAK_MAPPED  %>% group_indices(Lake) 
# 
# MAK_MAPPED <- MAK_MAPPED %>% mutate(LakeID=paste0("lake_",LakeID))
# 
# fulllakenames <- MAK_MAPPED %>% select(Lake,LakeID) %>% unique() %>%
#   filter(LakeID!="lake_11")
# 
# MAK_MAPPED_di<-Makroph_commLastYearfin %>% 
#   group_by(Lake) %>% 
#   summarise_at(vars(Callitriche.cophocarpa:Zannichellia.palustris), mean, na.rm = TRUE)
#   
# MAK_MAPPED_di$GAMMA <- vegan::specnumber(MAK_MAPPED_di[,c(2:72)])
# 
# MAK_MAPPED_din<-MAK_MAPPED_di %>%
#   select(Lake,GAMMA)%>%
#   mutate(GAMMAperc = GAMMA/MAK_MAPPED_NSPEC*100)
# 
# 
# MAK_MAPPED_din$LakeID <- MAK_MAPPED_din  %>% group_indices(Lake) 
# 
# MAK_MAPPED_din <- MAK_MAPPED_din %>% mutate(LakeID=paste0("lake_",LakeID))
```






Mean lake area per lake group
```{r}
data_lakes_env_class %>% 
  left_join(Morphology, by=c("LakeName"="Name_Makro_short") ) %>% 
  group_by(class) %>% 
  summarise(Area_mean_ha=mean(Area_ha), 
            maxDepth_mean_m=mean(maxDepth_m),
            Altitude_mean_masl=mean(Altitude_masl),
            CatchArea_mean_km2=mean(CatchmentArea_km2))

```



Number of Lakes per Lake group

```{r}
data_lakes_env_class %>% count(class) %>% kable() %>% kable_styling()
```






# Results
## Env conditions within scenarios
```{r}
data_lakes_env_classfuture<-data_lakes_env_class

data_lakes_env_classfuture$maxNut_m1 <- data_lakes_env_classfuture$maxNutrient-0.25*data_lakes_env_classfuture$maxNutrient

data_lakes_env_classfuture$maxNut_1 <- data_lakes_env_classfuture$maxNutrient+0.25*data_lakes_env_classfuture$maxNutrient

data_lakes_env_classfuture$maxkD_m1 <- data_lakes_env_classfuture$maxKd-0.25*data_lakes_env_classfuture$maxKd

data_lakes_env_classfuture$maxkD_1 <- data_lakes_env_classfuture$maxKd+0.25*data_lakes_env_classfuture$maxKd

data_lakes_env_classfuture$maxTemp_1 <- data_lakes_env_classfuture$maxTemp+1.5

data_lakes_env_classfuture$maxTemp_2 <- data_lakes_env_classfuture$maxTemp+3.0

meanEnv<-data_lakes_env_classfuture %>% group_by(class) %>% 
  select(latitude, maxNutrient, maxTemp, maxKd) %>%
  summarise_each(funs(mean, sd))

knitr::kable(meanEnv[,c(1:5)], digits = 4)
knitr::kable(meanEnv[,c(1,6:9)], digits = 4)



env_table<-data_lakes_env_classfuture %>% group_by(class) %>% 
  select(latitude, maxNutrient, maxTemp, maxKd)




M = cor(env_table %>% ungroup() %>% 
          select(latitude, maxNutrient,maxTemp,maxKd))
res1 <- cor.mtest(env_table %>% ungroup() %>% 
          select(latitude, maxNutrient,maxTemp,maxKd), conf.level = .95)
corrplot(M, #order = 'AOE', 
         addCoef.col = 'black', tl.pos = 'd',
         cl.pos = 'n', col = COL2('PiYG'),p.mat = res1$p, #sig.level = .2,
         insig = "label_sig",
         sig.level = c(.001, .01, .05), pch.cex=2, pch.col = "white")

```


## Q1 - Pot. species richness


### All together: N of species 
```{r, results='hide', message=FALSE}
surv_spec <- data %>%
  filter(Biomass_cat != 0) %>%
  distinct(Species)

NSPECtotal <- data %>% select(specNr) %>% unique() %>% count()
NLAKEStotal <- data %>% select(lakeNr) %>% unique() %>% count()

NSPECbase <- dim(surv_spec)[[1]]


```
In total, `r NSPECbase` species out of `r NSPECtotal` can grow in `r NLAKEStotal` real lakes. 
These `r NSPECbase` will be called as 100%. 




```{r message=FALSE, warning=FALSE}
Tv1<-data %>%
  #filter(Biomass_cat != 0) %>% 
  group_by(Group) %>%
  distinct(Species) %>% count(Group)

Tv2<-data %>%
  #filter(Biomass_cat != 0) %>% 
  group_by(Biomass_cat,Group) %>%
  distinct(Species) %>% count(Group) %>%
  spread("Biomass_cat","n") %>%
  rename("growing"="1")

d1nsp<-data %>%
  filter(depth_1 != 0) %>%
  group_by(Group) %>%
  distinct(Species) %>%
  count(Group) %>%
  rename("depth_1"="n")
  
d2nsp<-data %>%
  filter(depth_2 != 0) %>%
  group_by(Group) %>%
  distinct(Species) %>%
  count(Group) %>%
  rename("depth_2"="n")
d3nsp<-data %>%
  filter(depth_3 != 0) %>%
  group_by(Group) %>%
  distinct(Species) %>%
  count(Group) %>%
  rename("depth_3"="n")
d4nsp<-data %>%
  filter(depth_4 != 0) %>%
  group_by(Group) %>%
  distinct(Species) %>%
  count(Group) %>%
  rename("depth_4"="n")

NSpGroups<-left_join(Tv1, Tv2, by="Group") %>% 
  rename("space"="n") %>% select(-`0`) %>%
  left_join(d1nsp,by="Group") %>% left_join(d2nsp,by="Group") %>%
  left_join(d3nsp,by="Group")%>% left_join(d4nsp,by="Group") %>%
  mutate(growing_P=(growing/NSPECbase)*100)%>%
  mutate(depth_1_P=(depth_1/NSPECbase)*100)%>%
  mutate(depth_2_P=(depth_2/NSPECbase)*100)%>%
  mutate(depth_3_P=(depth_3/NSPECbase)*100)%>%
  mutate(depth_4_P=(depth_4/NSPECbase)*100)%>%
  select(-depth_1,-depth_2,-depth_3,-depth_4)

knitr::kable(NSpGroups, digits = 1)
```

Summarized for the whole dataset: 

Thus, it's a hump-shaped pattern of possible species richness of submerged macrophytes. 


How does that look like for real species 

```{r}

knitr::kable(MAK_grouped_depthindep_alllakes, digits = 1)
```







Complete N of species within the mapped datasets, just indicator species  `r MAK_MAPPED_NSPEC_indicationspec`




<br/><br/>

### Per lake: N of species 

```{r, results='hide', message=FALSE}
richLake<-data %>%
  group_by(Lake) %>%
  summarise_at(vars(Biomass_cat), ~ sum(. != 0)) %>%
  arrange(Biomass_cat) %>% # depth_1,depth_2,depth_3,depth_4,
  rename("Nspecies" = Biomass_cat) %>%
  filter(Nspecies==max(Nspecies))

richLakeName <- MAK_MAPPED %>% filter(LakeID==richLake$Lake) %>% select(Lake) %>% unique()

poorLake<-data %>%
  group_by(Lake) %>%
  summarise_at(vars(Biomass_cat), ~ sum(. != 0)) %>%
  arrange(Biomass_cat) %>% # depth_1,depth_2,depth_3,depth_4,
  rename("Nspecies" = Biomass_cat) %>%
  filter(Nspecies==min(Nspecies))

poorLakeName <- MAK_MAPPED %>% filter(LakeID==poorLake$Lake) %>% select(Lake) %>% unique()
```

Per lake between `r poorLake[1,2]` (`r poorLake[1,1]` in `r poorLakeName[1,1]`,  - `r round(poorLake[1,2]/NSPECbase*100, digits=2)` %) and `r richLake[1,2]` (`r richLake[1,1]`  in `r richLakeName`,   - `r round(richLake[1,2]/NSPECbase*100, digits=2)` %) species can grow.

Thus, we have a difference between lakes. 


```{r}
real_Barmsee <-MAK_grouped_depthindep %>% filter(Lake=="Barmsee") %>%
  filter(Group!="none") %>% ungroup() %>% summarise(NSPECperc=sum(NSPECperc))
```
Realised species richness Barmsee: `r real_Barmsee`



```{r}
real_Langbuerg<-MAK_grouped_depthindep %>% filter(Lake=="Langbuergner See") %>%
  filter(Group!="none") %>% ungroup() %>% summarise(NSPECperc=sum(NSPECperc))
```
Real. spec richness Langbürgner See: `r real_Langbuerg`




### Per lakes group
Potential
```{r}
Nspecies_P_groupes<-data %>%
  left_join((data_lakes_env_class %>% 
               select(Lake, class)%>%
               mutate(Lake=paste0("lake_",Lake))),
            by=c("Lake"))%>%
  group_by(class, specNr, Group) %>%
  summarise_at(vars(Biomass_cat), ~ sum(. != 0)) %>%
  mutate(Biomass_cat=ifelse(Biomass_cat>0,1,0))%>%
  
  ungroup() %>% group_by(class, Group) %>%
  summarise(Biomass_cat=sum(Biomass_cat)) %>%
  rename("Nspecies" = Biomass_cat) %>%
  mutate(Nspecies_P = (Nspecies/NSPECbase)*100) %>%
  select(-Nspecies) %>%
  spread(Group, Nspecies_P)

Nspecies_P_groupes_all<-data %>%
  left_join((data_lakes_env_class %>% 
               select(Lake, class)%>%
               mutate(Lake=paste0("lake_",Lake))),
            by=c("Lake"))%>%
  
  group_by(class, specNr) %>%
  summarise_at(vars(Biomass_cat), ~ sum(. != 0)) %>%
  mutate(Biomass_cat=ifelse(Biomass_cat>0,1,0))%>%
  
  ungroup() %>% group_by(class) %>%
  summarise(Biomass_cat=sum(Biomass_cat)) %>%
  rename("Nspecies" = Biomass_cat) %>%
  mutate(Nspecies_P_all = (Nspecies/NSPECbase)*100) %>%
  select(-Nspecies) 

knitr::kable(left_join(Nspecies_P_groupes,Nspecies_P_groupes_all, by="class"), digits = 1)


```




Realised % of species within lake groups and per species groups
```{r}
Nspaclakclass<-Makroph_comm_S %>%
  gather("Species", "Kohler",5:89) %>%
  mutate(Species = str_replace(Species, " ", "."))%>%
  left_join(GroupsSpecies, by = c("Species"="Taxon")) %>%
  select(-Trophie,-Typ, -Depth) %>%
  mutate(Gruppe = ifelse(is.na(Gruppe),"none", Gruppe)) %>%
  filter(!Lake %in% c("Altmuehlsee", "Drachensee", "Eixendorfer See",
                      "Grosser Brombachsee",
                     "Gruentensee","Igelsbachsee", "Kleiner Brombachsee",
                     "Liebensteinspeicher","Rottachsee",
                     "Steinberger See","Hofstaetter See",
                     "Untreusee","Walchensee","Murnersee","Rothsee",
                     "Seehamer See"))%>%
  rename(Group=Gruppe)%>%
  ungroup() %>%
  group_by(Lake) %>%
  filter(YEAR==max(YEAR))%>% #select last mapping per lake
  ungroup() %>%
  left_join(data_lakes_env_class, by=c("Lake"="LakeName")) %>%
  rename(LakeID=Lake.y) %>%
  
  
  group_by(Species, Group, class) %>%
  summarise_at(vars("Kohler"), sum, na.rm=T)%>% # Mean of Kohler per Lake, YEAR, Depth, Species and Group
  ungroup()%>%
  group_by(Group, class) %>%
  mutate(Kohler=ifelse(Kohler>0,1,0)) %>%
  summarise(NSPEC=sum(Kohler)) %>%
  mutate(NSPECperc = NSPEC/MAK_MAPPED_NSPEC_indicationspec$n*100) %>%
  select(-NSPEC)%>%
  spread(Group,NSPECperc)%>%
  rename(oligotrophic="1", mesotrophic="2", eutrophic="3")


Nspaclakclass_all<-Makroph_comm_S %>%
  gather("Species", "Kohler",5:89)%>%
  mutate(Species = str_replace(Species, " ", ".")) %>%
  left_join(GroupsSpecies, by = c("Species"="Taxon")) %>%
  select(-Trophie,-Typ, -Depth) %>%
  mutate(Gruppe = ifelse(is.na(Gruppe),"none", Gruppe)) %>%
  filter(!Lake %in% c("Altmuehlsee", "Drachensee", "Eixendorfer See",
                      "Grosser Brombachsee",
                     "Gruentensee","Igelsbachsee", "Kleiner Brombachsee",
                     "Liebensteinspeicher","Rottachsee",
                     "Steinberger See","Hofstaetter See",
                     "Untreusee","Walchensee","Murnersee","Rothsee",
                     "Seehamer See"))%>%
  rename(Group=Gruppe)%>%
  ungroup() %>%
  group_by(Lake) %>%
  filter(YEAR==max(YEAR))%>% #select last mapping per lake
  ungroup() %>%
  left_join(data_lakes_env_class, by=c("Lake"="LakeName")) %>%
  rename(LakeID=Lake.y) %>%
  filter(Group!="none")%>%
  
  group_by(Species, class) %>%
  summarise_at(vars("Kohler"), sum, na.rm=T)%>% # Mean of Kohler per Lake, YEAR, Depth, Species and Group
  ungroup()%>%
  group_by(class) %>%
  mutate(Kohler=ifelse(Kohler>0,1,0)) %>%
  summarise(NSPEC=sum(Kohler)) %>%
  mutate(NSPECperc_all = NSPEC/MAK_MAPPED_NSPEC_indicationspec$n*100) %>%
  select(-NSPEC)

knitr::kable(left_join(Nspaclakclass, Nspaclakclass_all, by="class"), digits = 1)

```




### Chi square test
```{r}
#Observed vrs potential 
OSRPSR<-left_join(Nspaclakclass, Nspecies_P_groupes, by="class") %>% select(-none)
samp<-as.data.frame(OSRPSR)
samp2 <- samp[,-1]
rownames(samp2) <- samp[,1]


olig<-samp2[c(1,6)]
chi<-chisq.test(olig)
chi

mesot<-samp2[c(2,5)]
chim<-chisq.test(mesot)
chim

eutro<-samp2[c(3,4)]
chie<-chisq.test(eutro)
chie



samp3<- as.data.frame(left_join(Nspaclakclass_all,Nspecies_P_groupes_all, by="class"))
 samp4 <- samp3[,-1]
rownames(samp4) <- samp3[,1]
 chiall<-chisq.test(samp4)
chiall
```


### FIG2 : DDG  


```{r}
lakesDDGModel<-data %>% 
  group_by(Lake, Group) %>%
  summarise_at(vars(depth_1, depth_2, depth_3, depth_4), ~ sum(. != 0)) %>%
  gather("depth", "NSpec", c(3:6))%>%
  mutate(NSpecP=(NSpec/NSPECbase)*100) %>% 
  select(-NSpec) %>%
  mutate(type="model")  

lakesDDGMapped <- MAK_mapped_grouped %>%
  mutate(depth=ifelse(Depth==-5.0, "depth_4", 
                      ifelse(Depth==-3.0, "depth_3",
                             ifelse(Depth==-1.5, "depth_2",
                                    ifelse(Depth==-0.5, "depth_1",NA))))) %>%
  mutate(type="mapped") %>% 
  rename(NSpecP=NSPECperc) %>% 
  ungroup() %>%
  select(-NSPEC, -Depth, -Lake) %>% 
  relocate(depth, .after = Group) %>%
  relocate(LakeID, .before = Group) %>%
  rename(Lake=LakeID) %>%
  filter(Group!="none")%>%
  mutate(Group=ifelse(Group==1, "oligotroph", 
                      ifelse(Group==2, "mesotroph", 
                             ifelse(Group==3, "eutroph", NA))))

lakesDDG2 = rbind(lakesDDGModel,lakesDDGMapped)

lakesDDG = lakesDDG2 %>% 
  left_join(fulllakenames, by=c("Lake"="LakeID")) %>%
  rename(LakeName = Lake.y) %>% 
  mutate(depth=ifelse(depth=="depth_1","-0.5",
                      ifelse(depth=="depth_2","-1.5",
                             ifelse(depth=="depth_3","-3.0",
                                    ifelse(depth=="depth_4","-5.0","NA"))))) %>%
  mutate(Group=ifelse(Group=="eutroph","eutraphentic",
                      ifelse(Group=="mesotroph","mesotraphentic",
                             ifelse(Group=="oligotroph","oligotraphentic","NA"))))
```




```{r, fig.height=9, fig.width=6}
my.formula <- y ~ x 

lakeclasses<-c("clear lakes","intermediate lakes", "turbid lakes")
names(lakeclasses)<-c("clear","medium","turb")


A1<-lakesDDG %>%
  filter(type=="model")%>%
  left_join((data_lakes_env_class %>% mutate(Lake=paste0("lake_",Lake)) %>%
               select(-LakeName)),
            by=c("Lake"))%>%
  ggplot(aes(depth, NSpecP, col=Group, group=interaction(Group,Lake)))+
  geom_path(alpha=0.5)+
  geom_boxplot(aes(group=interaction(depth,Group), fill=Group))+
  facet_grid(~class, 
              labeller = labeller(class = lakeclasses))+
  scale_colour_manual(values = c(rev(TrophiePalette)))+
  theme(legend.title = element_blank()) +
  xlab("Depth (m)")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  theme(legend.position = "none")+
  #ggtitle("Potential species richness (model)")+
  ylab("")+
  scale_fill_manual(values = c(rev(TrophiePalette)))+
  ylab("Potential \nspec. richness (%)")

A2<-lakesDDG %>%
  filter(type=="mapped")%>%
  left_join((data_lakes_env_class %>% mutate(Lake=paste0("lake_",Lake)) %>%
               select(-LakeName)),
            by=c("Lake"))%>%
  ggplot(aes(depth, NSpecP, col=Group, group=interaction(Group,Lake)))+
  geom_path(alpha=0.5)+
  geom_boxplot(aes(group=interaction(depth,Group), fill=Group))+
  facet_grid(~class, 
              labeller = labeller(class = lakeclasses))+
  scale_colour_manual(values = c(rev(TrophiePalette)))+
  theme(legend.title = element_blank()) +
  xlab("Depth (m)")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  theme(legend.position = "none")+
  #ggtitle("Realised species richness (mapped)")+
  scale_fill_manual(values = c(rev(TrophiePalette)))+
  ylab("Observed \nspec. richness (%)")


A3<-lakesDDG %>%
  #filter(type=="mapped")%>%
  left_join((data_lakes_env_class %>% mutate(Lake=paste0("lake_",Lake)) %>%
               select(-LakeName)),
            by=c("Lake")) %>%
  spread(type,NSpecP) %>%
  ggplot(aes(x=model,y=mapped, col=Group))+
  geom_point()+
  facet_grid(~class, 
              labeller = labeller(class = lakeclasses))+ #aes(col=Name)
  #geom_smooth(model=lm, method=lm, se=F, formula = my.formula,
  #            #aes(group=factor(depth), col=factor(depth))
  #            )+
  stat_correlation(vstep = 0.1,label.x = "centre")+
  #stat_poly_eq(formula = my.formula,
  #              eq.with.lhs = "italic(hat(y))~`=`~",
  #              aes(label = paste(..rr.label.., sep = "~~~")))+
  scale_colour_manual(values = c(rev(TrophiePalette)))+
  #ggtitle("comparison")+ 
  geom_abline(intercept = 0, slope = 1)+
  #annotate("text", x = 22, y = 25, label = "model = mapped", angle=34)+
  xlab("Potential spec. richness (%)")+
  ylab("Observed \nspec. richness (%)")+
  ylim(0,40)+xlim(0,40)




```
##### Fig2 plot
```{r, fig.height=8, fig.width=6.5}
FIG2<-((A2/A1) / A3) +theme(legend.position = "bottom")+ 
  labs(col="Spec. group") + 
  plot_annotation(tag_levels = 'a',
                  tag_prefix = '(',
                  tag_suffix = ')')& 
  theme(plot.tag = element_text(size = 12))& 
  guides(colour = guide_legend(override.aes = list(size=3)))

FIG2

#ggsave("Fig2.png", FIG2, width = 6.5, height=8, dpi="print", bg="white")


```


```{r}
lakesDDG %>%
  #filter(type=="mapped")%>%
  left_join((data_lakes_env_class %>% mutate(Lake=paste0("lake_",Lake)) %>%
               select(-LakeName)),
            by=c("Lake")) %>%
  spread(type,NSpecP)%>%
  mutate(potMINUSobserv=model-mapped)%>%
  mutate(error=ifelse(potMINUSobserv>0,"underestim",
                      ifelse(potMINUSobserv<0,"overestim",
                      "exact"))) %>%
  group_by(Group,class) %>%
  count(error)%>% 
  spread("error","n")
```





#### DDG for summary figure

```{r, fig.height=3, fig.width=7}
Fig5_part<-lakesDDG %>%
  filter(type=="model")%>%
  left_join((data_lakes_env_class %>% mutate(Lake=paste0("lake_",Lake)) %>%
               select(-LakeName)),
            by=c("Lake"))%>%
  group_by(Group,depth,class) %>%
  summarise(NSpecPmean=mean(NSpecP),NSpecPsd=sd(NSpecP))%>%
  ggplot(aes(depth, NSpecPmean, col=Group, group=interaction(Group)))+
  #geom_boxplot(aes(group=interaction(depth,Group), fill=Group))+
  facet_grid(~class, 
              labeller = labeller(class = lakeclasses))+
  geom_path(position=position_dodge(0.5), size=1)+
  geom_errorbar(aes(ymin=NSpecPmean-NSpecPsd, ymax=NSpecPmean+NSpecPsd), width=.2,
                 position=position_dodge(0.5))+

  scale_colour_manual(values = c(rev(TrophiePalette)))+
  theme(legend.title = element_blank()) +
  xlab("Depth (m)")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  theme(legend.position = "bottom")+
  #ggtitle("Potential species richness (model)")+
  scale_fill_manual(values = c(rev(TrophiePalette)))+
  ylab("Mean potential \nspec. richness (%)")

Fig5_part

#ggsave("Fig5_part.png", Fig5_part, width = 6.5, height=3, dpi="print", bg="white")
```


## Q2 - Scenarios

### All lakes together
#### Number of lost species per scenario [%]
```{r}
#Berechnung überprüft

NSPECbase<-scenario_data %>% select(speciesID) %>% unique() %>% nrow()

SPEC_DEAD <- all_diff_presabs_tobase %>% 
  group_by(speciesID) %>% select(-lakeID,-variable) %>%
  summarise_all(sum) %>% #Pro Art Summe aus Tiefen und Seen
  #filter(base>0) %>% #nur Arten, die schon vorkamen
  select(base,S0_m1,S0_1,S0_2,S1_m1,S1_0, S1_1,S1_2,S2_m1,S2_0,S2_1,S2_2) %>%
  summarise_all(funs(sum(. > 0, na.rm = TRUE))) %>% # N species pro Szen if present
  gather("scenario","Ntotspec",1:12) %>% 
  mutate(Lost= Ntotspec - NSPECbase) %>% 
  mutate(Lost_percent = (Lost/NSPECbase)*100) %>% 
  filter(scenario!="base") %>% 
  mutate(Temp=c(0,0,0,1,1,1,1,2,2,2,2)) %>%
  mutate(TurbN=c(-1,1,2,-1,0,1,2,-1,0,1,2)) %>% 
  select(-Ntotspec,-Lost,-scenario) %>%
  spread(TurbN,Lost_percent) %>% 
  rename("lostsp(%)"="Temp")

knitr::kable(SPEC_DEAD, digits = 1)%>% kable_styling()

```




#### Nspec lost per trophy group
```{r}
NSPECbaseGroup <- scenario_data %>% 
  filter(speciesID %in% c(14000:14300))%>% select(speciesID) %>% unique() %>% nrow()
SPEC_DEAD_group_oli <- all_diff_presabs_tobase %>% 
  filter(speciesID %in% c(14000:14300)) %>%
  group_by(speciesID) %>% select(-lakeID,-variable) %>%
  summarise_all(sum) %>% filter(base>0) %>% select(base,S0_m1,S0_1,S0_2,
                                                   S1_m1,S1_0, S1_1,S1_2,
                                                   S2_m1,S2_0,S2_1,S2_2) %>%
    summarise_all(funs(sum(. > 0, na.rm = TRUE))) %>%
  gather("scenario","Ntotspec",1:12) %>% 
  mutate(Lost= Ntotspec - NSPECbaseGroup) %>% 
  mutate(Lost_percent = (Lost/NSPECbaseGroup)*100) %>% 
  filter(scenario!="base") %>% 
  mutate(Temp=c(0,0,0,1,1,1,1,2,2,2,2)) %>%
  mutate(TurbN=c(-1,1,2,-1,0,1,2,-1,0,1,2)) %>% 
  select(-Ntotspec,-Lost,-scenario) %>%
  spread(TurbN,Lost_percent) %>% 
  rename("lostspOlig(%)"="Temp")

NSPECbaseGroup <- scenario_data %>% 
  filter(speciesID %in% c(15000:15300))%>% select(speciesID) %>% unique() %>% nrow()
SPEC_DEAD_group_meso <- all_diff_presabs_tobase %>% 
  filter(speciesID %in% c(15001:15300)) %>%
  group_by(speciesID) %>% select(-lakeID,-variable) %>%
  summarise_all(sum) %>% filter(base>0) %>% select(base,S0_m1,S0_1,S0_2,
                                                   S1_m1,S1_0, S1_1,S1_2,
                                                   S2_m1,S2_0,S2_1,S2_2) %>%
    summarise_all(funs(sum(. > 0, na.rm = TRUE))) %>%
  gather("scenario","Ntotspec",1:12) %>% 
  mutate(Lost= Ntotspec - NSPECbaseGroup) %>% 
  mutate(Lost_percent = (Lost/NSPECbaseGroup)*100) %>% 
  filter(scenario!="base") %>% 
  mutate(Temp=c(0,0,0,1,1,1,1,2,2,2,2)) %>%
  mutate(TurbN=c(-1,1,2,-1,0,1,2,-1,0,1,2)) %>% 
  select(-Ntotspec,-Lost,-scenario) %>%
  spread(TurbN,Lost_percent) %>% 
  rename("lostspMeso(%)"="Temp")

NSPECbaseGroup <- scenario_data %>% 
  filter(speciesID %in% c(16000:16300))%>% select(speciesID) %>% unique() %>% nrow()

SPEC_DEAD_group_eu <- all_diff_presabs_tobase %>% 
  filter(speciesID %in% c(16001:16300)) %>%
  group_by(speciesID) %>% select(-lakeID,-variable) %>%
  summarise_all(sum) %>% filter(base>0) %>% select(base,S0_m1,S0_1,S0_2,
                                                   S1_m1,S1_0, S1_1,S1_2,
                                                   S2_m1,S2_0,S2_1,S2_2) %>%
    summarise_all(funs(sum(. > 0, na.rm = TRUE))) %>%
  gather("scenario","Ntotspec",1:12) %>% 
  mutate(Lost= Ntotspec - NSPECbaseGroup) %>% 
  mutate(Lost_percent = (Lost/NSPECbaseGroup)*100) %>% 
  filter(scenario!="base") %>% 
  mutate(Temp=c(0,0,0,1,1,1,1,2,2,2,2)) %>%
  mutate(TurbN=c(-1,1,2,-1,0,1,2,-1,0,1,2)) %>% 
  select(-Ntotspec,-Lost,-scenario) %>%
  spread(TurbN,Lost_percent) %>% 
  rename("lostspeu(%)"="Temp")

knitr::kable(SPEC_DEAD_group_oli, digits = 1)%>% kable_styling()
knitr::kable(SPEC_DEAD_group_meso, digits = 1)%>% kable_styling()
knitr::kable(SPEC_DEAD_group_eu, digits = 1)%>% kable_styling()

```


s sterben unter heutigen Temperaturbedingungen mehr Arten aus, als wenn sich 
die Temperatur erhöht. 
Oligrotrophe Arten sind besonders betroffen vom Aussterben
Eutrophe Arten sterben unter klareren Bedingungen nur minimal aus


<br/><br/>

#### Per lake group
```{r}

all_diff_presabs_tobase %>%
  left_join((data_lakes_env_class %>% 
               select(Lake, class)),
            by=c("lakeID"="Lake"))%>% 
  group_by(speciesID, class) %>% select(-lakeID,-variable) %>%
  summarise_all(sum) %>% filter(base>0) %>% select(class,base,S0_m1,S0_1,S0_2,
                                                   S1_m1,S1_0, S1_1,S1_2,
                                                   S2_m1,S2_0,S2_1,S2_2) %>%
  mutate_at(vars(base,S0_m1,S0_1,S0_2,S1_m1,S1_0, S1_1,S1_2,
                 S2_m1,S2_0,S2_1,S2_2), ~ 1 * (. != 0)) %>%
  ungroup() %>% group_by(class) %>% select(-speciesID) %>%
  summarise_all(sum) %>%
    
  gather("scenario","Ntotspec",3:13) %>% 
  mutate(Lost= Ntotspec - base) %>% 
  mutate(Lost_percent = (Lost/base)*100) %>% select(-base,-Lost,-Ntotspec) %>%
  spread(class,Lost_percent) %>%
  kable() %>% kable_styling()
```




### Per lake and depth 

#### Mean Number of species per lake (+sd)
```{r, message=FALSE}

# Mean n of species per scenario ***
all_diff_prsabsMEAN <- all_diff_presabs_tobase %>%
  group_by(lakeID, speciesID) %>%
  summarise( #tiefenunabhängig Vorkommen in den Seen
    NspecXDepthsB = sum(base),
    NspecXDepthsS0_m1 = sum(S0_m1),
    NspecXDepthsS0_1 = sum(S0_1),
    NspecXDepthsS0_2 = sum(S0_2),
    NspecXDepthsS1_m1 = sum(S1_m1),
    NspecXDepthsS1_0 = sum(S1_0),
    NspecXDepthsS1_1 = sum(S1_1),
    NspecXDepthsS1_2 = sum(S1_2),
    NspecXDepthsS2_m1 = sum(S2_m1),
    NspecXDepthsS2_0 = sum(S2_0),
    NspecXDepthsS2_1 = sum(S2_1),
    NspecXDepthsS2_2 = sum(S2_2)
  ) %>%
  mutate_at(vars(NspecXDepthsB, NspecXDepthsS0_m1,NspecXDepthsS0_1, 
                 NspecXDepthsS0_2, 
                 NspecXDepthsS1_m1, NspecXDepthsS1_0, 
                 NspecXDepthsS1_1, NspecXDepthsS1_2,
                 NspecXDepthsS2_m1,NspecXDepthsS2_0,
                 NspecXDepthsS2_1,NspecXDepthsS2_2), ~ 1 * (. != 0)) %>% # Pres/Abs
  ungroup() %>%
  group_by(lakeID) %>%
  summarise( #Arten pro See
    base = sum(NspecXDepthsB),
    S0_m1 = sum(NspecXDepthsS0_m1),
    S0_1 = sum(NspecXDepthsS0_1),
    S0_2 = sum(NspecXDepthsS0_2),
    S1_m1 = sum(NspecXDepthsS1_m1),
    S1_0 = sum(NspecXDepthsS1_0),
    S1_1 = sum(NspecXDepthsS1_1),
    S1_2 = sum(NspecXDepthsS1_2),
    S2_m1 = sum(NspecXDepthsS2_m1),
    S2_0 = sum(NspecXDepthsS2_0),
    S2_1 = sum(NspecXDepthsS2_1),
    S2_2 = sum(NspecXDepthsS2_2)
  ) %>%
  gather("scenario", "NSpec", 2:13) %>%
  group_by(scenario)  %>% 
  summarise(NSpMean = mean(NSpec))%>%
  arrange(factor(scenario, 
                 levels = c("S0_m1","base","S0_1","S0_2","S1_m1",
                            "S1_0","S1_1","S1_2",
                                      "S2_m1","S2_0","S2_1","S2_2")))

all_diff_prsabsSD <- all_diff_presabs_tobase %>%
  group_by(lakeID, speciesID) %>%
  summarise(
    NspecXDepthsB = sum(base),
    NspecXDepthsS0_m1 = sum(S0_m1),
    NspecXDepthsS0_1 = sum(S0_1),
    NspecXDepthsS0_2 = sum(S0_2),
    NspecXDepthsS1_m1 = sum(S1_m1),
    NspecXDepthsS1_0 = sum(S1_0),
    NspecXDepthsS1_1 = sum(S1_1),
    NspecXDepthsS1_2 = sum(S1_2),
    NspecXDepthsS2_m1 = sum(S2_m1),
    NspecXDepthsS2_0 = sum(S2_0),
    NspecXDepthsS2_1 = sum(S2_1),
    NspecXDepthsS2_2 = sum(S2_2)
  ) %>%
  mutate_at(vars(NspecXDepthsB, NspecXDepthsS0_m1,NspecXDepthsS0_1, 
                 NspecXDepthsS0_2, 
                 NspecXDepthsS1_m1, NspecXDepthsS1_0, 
                 NspecXDepthsS1_1, NspecXDepthsS1_2,
                 NspecXDepthsS2_m1,NspecXDepthsS2_0,NspecXDepthsS2_1,
                 NspecXDepthsS2_2), ~ 1 * (. != 0)) %>%
  ungroup() %>%
  group_by(lakeID) %>%
  summarise(
    base = sum(NspecXDepthsB),
    S0_m1 = sum(NspecXDepthsS0_m1),
    S0_1 = sum(NspecXDepthsS0_1),
    S0_2 = sum(NspecXDepthsS0_2),
    S1_m1 = sum(NspecXDepthsS1_m1),
    S1_0 = sum(NspecXDepthsS1_0),
    S1_1 = sum(NspecXDepthsS1_1),
    S1_2 = sum(NspecXDepthsS1_2),
    S2_m1 = sum(NspecXDepthsS2_m1),
    S2_0 = sum(NspecXDepthsS2_0),
    S2_1 = sum(NspecXDepthsS2_1),
    S2_2 = sum(NspecXDepthsS2_2)
  ) %>%
  gather("scenario", "NSpec", 2:13) %>%
  group_by(scenario)  %>% 
  summarise(NSpMean = sd(NSpec))%>%
  arrange(factor(scenario, 
                 levels = c("S0_m1","base","S0_1","S0_2","S1_m1",
                            "S1_0","S1_1","S1_2",
                            "S2_m1","S2_0","S2_1","S2_2")))

knitr::kable(all_diff_prsabsMEAN %>% mutate(Temp=c(0,0,0,0,1,1,1,1,2,2,2,2),
                               NutTurb=c(-1,0,1,2,-1,0,1,2,-1,0,1,2)) %>%
  select(-scenario) %>%
  spread(NutTurb,NSpMean) %>% rename("meanSpN"="Temp"), digits = 1)%>% kable_styling()

knitr::kable(all_diff_prsabsSD %>% mutate(Temp=c(0,0,0,0,1,1,1,1,2,2,2,2),
                               NutTurb=c(-1,0,1,2,-1,0,1,2,-1,0,1,2)) %>%
  select(-scenario) %>%
  spread(NutTurb,NSpMean) %>% rename("sdSpN"="Temp"), 
  digits = 1) %>% kable_styling()

# all_diff_presabs_tobase %>%
#   group_by(speciesID) %>% summarise(base=sum(base))

```

Im Mittel können unter CC mehr Arten potentiell in Bayern wachsen. 


#### Mean Number of species per lake and species group
For oligotroph

```{r}
# Mean n of species per scenario ***
all_diff_prsabsMEAN_o <- all_diff_presabs_tobase %>%
  filter(speciesID %in% c(14000:14300)) %>% 
  group_by(lakeID, speciesID) %>%
  summarise(
    NspecXDepthsB = sum(base),
    NspecXDepthsS0_m1 = sum(S0_m1),
    NspecXDepthsS0_1 = sum(S0_1),
    NspecXDepthsS0_2 = sum(S0_2),
    NspecXDepthsS1_m1 = sum(S1_m1),
    NspecXDepthsS1_0 = sum(S1_0),
    NspecXDepthsS1_1 = sum(S1_1),
    NspecXDepthsS1_2 = sum(S1_2),
    NspecXDepthsS2_m1 = sum(S2_m1),
    NspecXDepthsS2_0 = sum(S2_0),
    NspecXDepthsS2_1 = sum(S2_1),
    NspecXDepthsS2_2 = sum(S2_2)
  ) %>%
  mutate_at(vars(NspecXDepthsB, NspecXDepthsS0_m1,NspecXDepthsS0_1, 
                 NspecXDepthsS0_2, 
                 NspecXDepthsS1_m1, NspecXDepthsS1_0, 
                 NspecXDepthsS1_1, NspecXDepthsS1_2,
                 NspecXDepthsS2_m1,NspecXDepthsS2_0,
                 NspecXDepthsS2_1,NspecXDepthsS2_2), ~ 1 * (. != 0)) %>%
  ungroup() %>%
  group_by(lakeID) %>%
  summarise(
    base = sum(NspecXDepthsB),
    S0_m1 = sum(NspecXDepthsS0_m1),
    S0_1 = sum(NspecXDepthsS0_1),
    S0_2 = sum(NspecXDepthsS0_2),
    S1_m1 = sum(NspecXDepthsS1_m1),
    S1_0 = sum(NspecXDepthsS1_0),
    S1_1 = sum(NspecXDepthsS1_1),
    S1_2 = sum(NspecXDepthsS1_2),
    S2_m1 = sum(NspecXDepthsS2_m1),
    S2_0 = sum(NspecXDepthsS2_0),
    S2_1 = sum(NspecXDepthsS2_1),
    S2_2 = sum(NspecXDepthsS2_2)
  ) %>%
  gather("scenario", "NSpec", 2:13) %>%
  group_by(scenario)  %>% 
  summarise(NSpMean = mean(NSpec))%>%
  arrange(factor(scenario, 
                 levels = c("S0_m1","base","S0_1","S0_2","S1_m1",
                            "S1_0","S1_1","S1_2",
                                      "S2_m1","S2_0","S2_1","S2_2")))

all_diff_prsabsMEAN_m <- all_diff_presabs_tobase %>%
  filter(speciesID %in% c(15001:15300)) %>% 
  group_by(lakeID, speciesID) %>%
  summarise(
    NspecXDepthsB = sum(base),
    NspecXDepthsS0_m1 = sum(S0_m1),
    NspecXDepthsS0_1 = sum(S0_1),
    NspecXDepthsS0_2 = sum(S0_2),
    NspecXDepthsS1_m1 = sum(S1_m1),
    NspecXDepthsS1_0 = sum(S1_0),
    NspecXDepthsS1_1 = sum(S1_1),
    NspecXDepthsS1_2 = sum(S1_2),
    NspecXDepthsS2_m1 = sum(S2_m1),
    NspecXDepthsS2_0 = sum(S2_0),
    NspecXDepthsS2_1 = sum(S2_1),
    NspecXDepthsS2_2 = sum(S2_2)
  ) %>%
  mutate_at(vars(NspecXDepthsB, NspecXDepthsS0_m1,NspecXDepthsS0_1, 
                 NspecXDepthsS0_2, 
                 NspecXDepthsS1_m1, NspecXDepthsS1_0, 
                 NspecXDepthsS1_1, NspecXDepthsS1_2,
                 NspecXDepthsS2_m1,NspecXDepthsS2_0,
                 NspecXDepthsS2_1,NspecXDepthsS2_2), ~ 1 * (. != 0)) %>%
  ungroup() %>%
  group_by(lakeID) %>%
  summarise(
    base = sum(NspecXDepthsB),
    S0_m1 = sum(NspecXDepthsS0_m1),
    S0_1 = sum(NspecXDepthsS0_1),
    S0_2 = sum(NspecXDepthsS0_2),
    S1_m1 = sum(NspecXDepthsS1_m1),
    S1_0 = sum(NspecXDepthsS1_0),
    S1_1 = sum(NspecXDepthsS1_1),
    S1_2 = sum(NspecXDepthsS1_2),
    S2_m1 = sum(NspecXDepthsS2_m1),
    S2_0 = sum(NspecXDepthsS2_0),
    S2_1 = sum(NspecXDepthsS2_1),
    S2_2 = sum(NspecXDepthsS2_2)
  ) %>%
  gather("scenario", "NSpec", 2:13) %>%
  group_by(scenario)  %>% 
  summarise(NSpMean = mean(NSpec))%>%
  arrange(factor(scenario, 
                 levels = c("S0_m1","base","S0_1","S0_2","S1_m1",
                            "S1_0","S1_1","S1_2",
                                      "S2_m1","S2_0","S2_1","S2_2")))

all_diff_prsabsMEAN_e <- all_diff_presabs_tobase %>%
  filter(speciesID %in% c(16001:16300)) %>% 
  group_by(lakeID, speciesID) %>%
  summarise(
    NspecXDepthsB = sum(base),
    NspecXDepthsS0_m1 = sum(S0_m1),
    NspecXDepthsS0_1 = sum(S0_1),
    NspecXDepthsS0_2 = sum(S0_2),
    NspecXDepthsS1_m1 = sum(S1_m1),
    NspecXDepthsS1_0 = sum(S1_0),
    NspecXDepthsS1_1 = sum(S1_1),
    NspecXDepthsS1_2 = sum(S1_2),
    NspecXDepthsS2_m1 = sum(S2_m1),
    NspecXDepthsS2_0 = sum(S2_0),
    NspecXDepthsS2_1 = sum(S2_1),
    NspecXDepthsS2_2 = sum(S2_2)
  ) %>%
  mutate_at(vars(NspecXDepthsB, NspecXDepthsS0_m1,NspecXDepthsS0_1, 
                 NspecXDepthsS0_2, 
                 NspecXDepthsS1_m1, NspecXDepthsS1_0, 
                 NspecXDepthsS1_1, NspecXDepthsS1_2,
                 NspecXDepthsS2_m1,NspecXDepthsS2_0,
                 NspecXDepthsS2_1,NspecXDepthsS2_2), ~ 1 * (. != 0)) %>%
  ungroup() %>%
  group_by(lakeID) %>%
  summarise(
    base = sum(NspecXDepthsB),
    S0_m1 = sum(NspecXDepthsS0_m1),
    S0_1 = sum(NspecXDepthsS0_1),
    S0_2 = sum(NspecXDepthsS0_2),
    S1_m1 = sum(NspecXDepthsS1_m1),
    S1_0 = sum(NspecXDepthsS1_0),
    S1_1 = sum(NspecXDepthsS1_1),
    S1_2 = sum(NspecXDepthsS1_2),
    S2_m1 = sum(NspecXDepthsS2_m1),
    S2_0 = sum(NspecXDepthsS2_0),
    S2_1 = sum(NspecXDepthsS2_1),
    S2_2 = sum(NspecXDepthsS2_2)
  ) %>%
  gather("scenario", "NSpec", 2:13) %>%
  group_by(scenario)  %>% 
  summarise(NSpMean = mean(NSpec))%>%
  arrange(factor(scenario, 
                 levels = c("S0_m1","base","S0_1","S0_2","S1_m1",
                            "S1_0","S1_1","S1_2",
                                      "S2_m1","S2_0","S2_1","S2_2")))

knitr::kable(all_diff_prsabsMEAN_o %>% 
               mutate(Temp=c(0,0,0,0,1,1,1,1,2,2,2,2),
                      NutTurb=c(-1,0,1,2,-1,0,1,2,-1,0,1,2)) %>%
               select(-scenario) %>%
               spread(NutTurb,NSpMean) %>% 
               rename("meanSpN_oligo"="Temp"), digits = 1)%>% kable_styling()

knitr::kable(all_diff_prsabsMEAN_m %>% 
               mutate(Temp=c(0,0,0,0,1,1,1,1,2,2,2,2),
                      NutTurb=c(-1,0,1,2,-1,0,1,2,-1,0,1,2)) %>%
               select(-scenario) %>%
               spread(NutTurb,NSpMean) %>% 
               rename("meanSpN_meso"="Temp"), digits = 1)%>% kable_styling()

knitr::kable(all_diff_prsabsMEAN_e %>% 
               mutate(Temp=c(0,0,0,0,1,1,1,1,2,2,2,2),
                      NutTurb=c(-1,0,1,2,-1,0,1,2,-1,0,1,2)) %>%
               select(-scenario) %>%
               spread(NutTurb,NSpMean) %>% 
               rename("meanSpN_eu"="Temp"), digits = 1)%>% kable_styling()
```





#### FIG3
```{r}
#PANEL B TURB/NUTR
scentunutlabel<-c(TurbNutm1="-25%",TurbNut1="+25%")#
Fig3B<-all_diff_presabs_tobase %>% 
  left_join(data_lakes_env_class %>% select(Lake,class), by=c("lakeID"="Lake")) %>%
  mutate(Trophie = ifelse(speciesID %in% c(14001:14300), "oligotraphentic",
                          ifelse(speciesID %in% c(15001:15300), "mesotraphentic",
                                 ifelse(speciesID %in% c(16001:16300), "eutraphentic",NA))))%>%

  group_by(lakeID, variable,Trophie, class) %>% 
  summarise( #pro See und Tiefe Anzahl der Arten
    base = sum(base),
    S0m1 = sum(S0_m1),
    S01 = sum(S0_1),
    S02 = sum(S0_2),
    S1m1 = sum(S1_m1),
    S10 = sum(S1_0),
    S11 = sum(S1_1),
    S12 = sum(S1_2),
    S2m1 = sum(S2_m1),
    S20 = sum(S2_0),
    S21 = sum(S2_1),
    S22 = sum(S2_2)
   ) %>%
    mutate(
    S0m1minusBaseP = (S0m1 - base),
    S01minusBaseP = (S01 - base),
    S02minusBaseP = (S02 - base),
    S1m1minusBaseP = (S1m1- base),
    S10minusBaseP = (S10 - base),
    S11minusBaseP = (S11 - base),
    S12minusBaseP = (S12 - base),
    S2m1minusBaseP = (S2m1 - base),
    S20minusBaseP = (S20 - base),
    S21minusBaseP = (S21 - base),
    S22minusBaseP = (S22 - base)
  )%>% 
  ungroup() %>%
  group_by(variable,Trophie, class) %>% 
  select(-lakeID, -S0m1,-S01,-S02,-S1m1,-S10,-S11, -S12,-S2m1,-S20,-S21,-S22) %>%
  summarise_all(list(mean=mean, sd=sd)) %>%
  gather("scenario", "NSpec", c(5:15,17:27)) %>% 
  mutate(type=str_extract(scenario,"[^_]+$"),
         scenario=str_extract(scenario, "[^_]+")) %>%
  spread(type, NSpec) %>%
  
  mutate(scenarioTemp = ifelse(scenario=="base" | scenario=="S01minusBaseP" | 
                              scenario=="S02minusBaseP" | scenario=="S0m1minusBaseP", "Temp0", 
                    ifelse(scenario=="S10minusBaseP" | scenario=="S11minusBaseP" | 
                          scenario=="S12minusBaseP" | scenario=="S1m1minusBaseP", "Temp1",
                    ifelse(scenario=="S20minusBaseP" | scenario=="S21minusBaseP" |
                           scenario=="S22minusBaseP" | scenario=="S2m1minusBaseP",
                           "Temp2",NA)))) %>%
  mutate(scenarioTurbNut = ifelse(scenario=="base" | scenario=="S10minusBaseP" |
                                  scenario=="S20minusBaseP", "TurbNut0", 
                           ifelse(scenario=="S0m1minusBaseP" | scenario=="S1m1minusBaseP" |
                                        scenario=="S2m1minusBaseP", "TurbNutm1",
                           ifelse(scenario=="S01minusBaseP" | scenario=="S11minusBaseP" |
                                               scenario=="S21minusBaseP", "TurbNut1",
                           ifelse(scenario=="S02minusBaseP" | scenario=="S12minusBaseP" |
                                                      scenario=="S22minusBaseP", 
                                                    "TurbNut2", NA ))))) %>%
  filter(scenarioTemp=="Temp0")%>%
  filter(scenarioTurbNut!="TurbNut2")%>%

  ggplot(aes(factor(variable),mean, 
             group=interaction(Trophie, scenarioTemp)))+#, col=factor(Trophie
    geom_point(aes(col=interaction(Trophie)),
                position=position_dodge(width=0.5))+
  geom_path(alpha=0.5, aes(col=interaction(Trophie)),
                position=position_dodge(width=0.5))+
  #geom_bar(stat="identity", aes(fill=factor(Trophie)), 
  #         position = position_dodge(width=0.5),
  #         width=0.5)+
  geom_errorbar(aes(ymax=mean+sd,
                    ymin=mean-sd,
                    col=interaction(Trophie)),
                position=position_dodge(width=0.5), width=.2)+
  #geom_boxplot()+
  facet_grid(scenarioTurbNut~class, 
              labeller = labeller(class = lakeclasses,
                                  scenarioTurbNut = scentunutlabel))+
  ylab("Potential spec. \nrichness change (N)")+
  theme(legend.position = "bottom")+
  scale_color_manual(values=rev(TrophiePalette))+
  theme(legend.title = element_blank())+
  scale_x_discrete(limits=rev)+ 
  geom_hline(yintercept=0, linetype="dashed", color = "red")+
  xlab("Depth (m)")+
  scale_y_continuous(
    sec.axis = dup_axis(name = expression(increase %<-% TurbNutr %->% decrease), 
                        breaks = NULL))+ 
  theme(axis.title.y.right = element_text(size=10,color = "grey50"))
```

```{r}
#PANEL A TEMPERATURE
scentemplabel<-c(Temp1="+1.5°C",Temp2="+3°C")#
Fig3A<-all_diff_presabs_tobase %>% 
  left_join(data_lakes_env_class %>% select(Lake,class), by=c("lakeID"="Lake")) %>%
  mutate(Trophie = ifelse(speciesID %in% c(14001:14300), "oligotraphentic",
                          ifelse(speciesID %in% c(15001:15300), "mesotraphentic",
                                 ifelse(speciesID %in% c(16001:16300), "eutraphentic",NA))))%>%

  group_by(lakeID, variable,Trophie, class) %>% 
  summarise( #pro See und Tiefe Anzahl der Arten
    base = sum(base),
    S0m1 = sum(S0_m1),
    S01 = sum(S0_1),
    S02 = sum(S0_2),
    S1m1 = sum(S1_m1),
    S10 = sum(S1_0),
    S11 = sum(S1_1),
    S12 = sum(S1_2),
    S2m1 = sum(S2_m1),
    S20 = sum(S2_0),
    S21 = sum(S2_1),
    S22 = sum(S2_2)
   ) %>%
    mutate(
    S0m1minusBaseP = (S0m1 - base),
    S01minusBaseP = (S01 - base),
    S02minusBaseP = (S02 - base),
    S1m1minusBaseP = (S1m1- base),
    S10minusBaseP = (S10 - base),
    S11minusBaseP = (S11 - base),
    S12minusBaseP = (S12 - base),
    S2m1minusBaseP = (S2m1 - base),
    S20minusBaseP = (S20 - base),
    S21minusBaseP = (S21 - base),
    S22minusBaseP = (S22 - base)
  )%>% 
  ungroup() %>%
  group_by(variable,Trophie, class) %>% 
  select(-lakeID, -S0m1,-S01,-S02,-S1m1,-S10,-S11, -S12,-S2m1,-S20,-S21,-S22) %>%
  summarise_all(list(mean=mean, sd=sd)) %>%
  
  
  gather("scenario", "NSpec", c(5:15,17:27)) %>% 
  mutate(type=str_extract(scenario,"[^_]+$"),
         scenario=str_extract(scenario, "[^_]+")) %>%
  spread(type, NSpec) %>%

  
  mutate(scenarioTemp = ifelse(scenario=="base" | scenario=="S01minusBaseP" | 
                              scenario=="S02minusBaseP" | scenario=="S0m1minusBaseP", "Temp0", 
                    ifelse(scenario=="S10minusBaseP" | scenario=="S11minusBaseP" | 
                          scenario=="S12minusBaseP" | scenario=="S1m1minusBaseP", "Temp1",
                    ifelse(scenario=="S20minusBaseP" | scenario=="S21minusBaseP" |
                           scenario=="S22minusBaseP" | scenario=="S2m1minusBaseP",
                           "Temp2",NA)))) %>%
  mutate(scenarioTurbNut = ifelse(scenario=="base" | scenario=="S10minusBaseP" |
                                  scenario=="S20minusBaseP", "TurbNut0", 
                           ifelse(scenario=="S0m1minusBaseP" | scenario=="S1m1minusBaseP" |
                                        scenario=="S2m1minusBaseP", "TurbNutm1",
                           ifelse(scenario=="S01minusBaseP" | scenario=="S11minusBaseP" |
                                               scenario=="S21minusBaseP", "TurbNut1",
                           ifelse(scenario=="S02minusBaseP" | scenario=="S12minusBaseP" |
                                                      scenario=="S22minusBaseP", 
                                                    "TurbNut2", NA ))))) %>%

  filter(scenarioTurbNut=="TurbNut0")%>%

  ggplot(aes(factor(variable),mean, 
             group=interaction(Trophie, scenarioTemp)))+#, col=factor(Trophie
  geom_point(aes(col=interaction(Trophie)),
                position=position_dodge(width=0.5))+
  geom_path(alpha=0.5, aes(col=interaction(Trophie)),
                position=position_dodge(width=0.5))+
  #geom_bar(stat="identity", aes(fill=factor(Trophie)), 
  #         position = position_dodge(width=0.5),
  #         width=0.5)+
  geom_errorbar(aes(ymax=mean+sd,
                    ymin=mean-sd,
                    col=interaction(Trophie)),
                position=position_dodge(width=0.5), width=.2)+
  #geom_boxplot()+
  facet_grid(scenarioTemp~class, 
              labeller = labeller(class = lakeclasses, 
                                  scenarioTemp = scentemplabel))+
  ylab("Potential spec. \nrichness change (N)")+
  theme(legend.position = "bottom")+
  scale_color_manual(values=rev(TrophiePalette))+
  theme(legend.title = element_blank())+
  scale_x_discrete(limits=rev)+ 
  geom_hline(yintercept=0, linetype="dashed", color = "red")+
  xlab("Depth (m)") +
  scale_y_continuous(limits=c(-5,20),breaks = seq(0, 20, 10),
    sec.axis = dup_axis(name = expression(Temperature %->% increasing), 
                        breaks = NULL))+ 
  theme(axis.title.y.right = element_text(size=10,color = "grey50"),
        legend.position = "bottom")
```

```{r, fig.height=7, fig.width=5}
# #COMBINE PLOTS WITHOUT PANEL C
# ((Fig3A + xlab(""))/ 
#    (Fig3B)) + 
#   plot_annotation(tag_levels = 'A')+ 
#   #labs(col="Spec. group") + 
#   plot_layout(heights = c(1, 3)) + 
#   plot_layout(guides = "collect") &
#   theme(legend.position = "bottom",                                              strip.text.x = element_text(size = 8),
#                 strip.text.y = element_text(size = 10),
#                 axis.text.x = element_text(angle = 90, 
#                                            vjust = 0.5, hjust=1),
#                 axis.title=element_text(size=10))
```


```{r}
# PANEL C TRY Interactive effect of Temp and water quality
Fig3C<-all_diff_presabs_tobase %>% 
  left_join(data_lakes_env_class %>% select(Lake,class), by=c("lakeID"="Lake")) %>%
  mutate(Trophie = ifelse(speciesID %in% c(14001:14300), "oligotraphentic",
                          ifelse(speciesID %in% c(15001:15300), "mesotraphentic",
                                 ifelse(speciesID %in% c(16001:16300), "eutraphentic",NA))))%>%

  group_by(lakeID, variable,Trophie, class) %>% 
  summarise( #pro See und Tiefe Anzahl der Arten
    base = sum(base),
    S0m1 = sum(S0_m1),
    S01 = sum(S0_1),
    S02 = sum(S0_2),
    S1m1 = sum(S1_m1),
    S10 = sum(S1_0),
    S11 = sum(S1_1),
    S12 = sum(S1_2),
    S2m1 = sum(S2_m1),
    S20 = sum(S2_0),
    S21 = sum(S2_1),
    S22 = sum(S2_2)
   ) %>%
    mutate(
    S0m1minusBaseP = (S0m1 - base),
    S01minusBaseP = (S01 - base),
    S02minusBaseP = (S02 - base),
    S1m1minusBaseP = (S1m1- base),
    S10minusBaseP = (S10 - base),
    S11minusBaseP = (S11 - base),
    S12minusBaseP = (S12 - base),
    S2m1minusBaseP = (S2m1 - base),
    S20minusBaseP = (S20 - base),
    S21minusBaseP = (S21 - base),
    S22minusBaseP = (S22 - base)
  )%>% 
  mutate(S2m1IC = S2m1minusBaseP-(S0m1minusBaseP + S20minusBaseP),
         S1m1IC = S1m1minusBaseP-(S0m1minusBaseP + S10minusBaseP),
         S21IC = S21minusBaseP-(S01minusBaseP + S20minusBaseP),
         S11IC = S11minusBaseP-(S01minusBaseP + S10minusBaseP)) %>%
  
  ungroup() %>%
  group_by(variable,Trophie, class) %>% 
  select(class,Trophie,variable,S2m1IC,S1m1IC,S21IC,S11IC ) %>%
  summarise_all(list(mean=mean, sd=sd)) %>%
  
  
  gather("scenario", "NSpec", c(4:11)) %>% 
  mutate(type=str_extract(scenario,"[^_]+$"),
         scenario=str_extract(scenario, "[^_]+")) %>%
  spread(type, NSpec) %>%
  filter(scenario=="S2m1IC" | scenario=="S21IC")%>%
  mutate(scenario=ifelse(scenario=="S2m1IC","+3°C\n-25%","+3°C\n+25%")) %>%

  ggplot(aes(factor(variable),mean, 
             group=interaction(Trophie)))+
  geom_point(aes(col=interaction(Trophie)),
                position=position_dodge(width=0.5))+
  geom_path(alpha=0.5, aes(col=interaction(Trophie)),
                position=position_dodge(width=0.5))+

  geom_errorbar(aes(ymax=mean+sd,
                    ymin=mean-sd,
                    col=interaction(Trophie)),
                position=position_dodge(width=0.5), width=.2)+
  #geom_boxplot()+
  facet_grid(scenario~class, 
              labeller = labeller(class = lakeclasses))+
  ylab("INTERACTIVE potential spec. \nrichness change (N)")+
  theme(legend.position = "bottom")+
  scale_color_manual(values=rev(TrophiePalette))+
  theme(legend.title = element_blank())+
  scale_x_discrete(limits=rev)+ 
  geom_hline(yintercept=0, linetype="dashed", color = "red")+
  xlab("Depth (m)") +
  scale_y_continuous(limits=c(-10,10),
                     breaks = seq(-10, 10, 10),
    sec.axis = dup_axis(name = expression(decrease %<-% NutTurb %->% incr), 
                        breaks = NULL))+ 
  theme(axis.title.y.right = element_text(size=10,color = "grey50"),
        legend.position = "bottom")#+
  #ggtitle("Interactive effect of Temp increase (+3°C) and NutTurb in/decrease")
```


###### plot
```{r, fig.height=8.0, fig.width=6.5}
#COMBINE PLOTS
FIG3fin<-((Fig3A + xlab(""))/ 
   (Fig3B + xlab("")) /
   (Fig3C )) + 
  plot_annotation(tag_levels = 'a',
                  tag_prefix = '(',
                  tag_suffix = ')')+ 
  #labs(col="Spec. group") + 
  plot_layout(heights = c(1, 2, 1)) + 
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom",                                              
        strip.text.x = element_text(size = 8),
                strip.text.y = element_text(size = 10),
                axis.text.x = element_text(angle = 90, 
                                           vjust = 0.5, hjust=1),
                axis.title=element_text(size=10))& 
  theme(plot.margin =  unit(c(-0.0, 0.2, -0.0, 0.2), "cm"),
        plot.tag = element_text(size = 12))& 
  guides(colour = guide_legend(override.aes = list(size=2)))

FIG3fin

# ggsave("Fig3.png", FIG3fin, width = 6.5, height=8, dpi="print", bg="white")
```



#### Win and Lost of species

Alte Analyse, die cih hier mal lasse, weil sie nett ist. 


```{r, fig.height=10}

scen.labs <- c("S0_m1", "base"," S0_1", "SO_2", "S1_m1", "S1_0", "S1_1","S1_2", "S2_m1 *", 
               "S2_0", "S2_1 *","S2_2")

scen.labs.Turb <- c("TurbNutr_m1","TurbNutr_0","TurbNutr_1","TurbNutr_2")
names(scen.labs.Turb)<- c("TurbNutr_m1","TurbNutr_0","TurbNutr_1","TurbNutr_2")

names(scen.labs) <- c("S0_m1minusBase", "base","S0_1minusBase", "S0_2minusBase", 
                      "S1_m1minusBase", "S1_0minusBase", "S1_1minusBase", "S1_2minusBase", 
                      "S2_m1minusBase", "S2_0minusBase", "S2_1minusBase", "S2_2minusBase")
presabs.labs <- c("Loss", "Increase")
names(presabs.labs) <- c("-1", "1")

scen2.labs <- c("S2_m1 *", "S2_N0_Tm1"," S2_N1_Tm1", 
                "S2_Nm1_T0", "S2_0", "S2_N1_T0", 
                "S2_Nm1_T1","S2_N0_T1", "S2_1 *")
names(scen2.labs) <- c("S2_m1minusS2_0",
      "S2_N0_Tm1minusS2_0",
      "S2_N1_Tm1minusS2_0",
      "S2_Nm1_T0minusS2_0",
      "S2_0",
      "S2_N1_T0minusS2_0",
      "S2_Nm1_T1minusS2_0",
      "S2_N0_T1minusS2_0",
      "S2_1minusS2_0")

annotate_background <- tibble(
  scenario = scen.labs,
  color = "blue",
  variable = -2
)


Nspec_base_perdepth <-all_diff_presabs_tobase %>%
  group_by(lakeID, variable) %>%
  summarise(
    base = sum(base),
    S0_m1 = sum(S0_m1),
    S0_1 = sum(S0_1),
    S0_2 = sum(S0_2),
    S1_m1 = sum(S1_m1),
    S1_0 = sum(S1_0),
    S1_1 = sum(S1_1),
    S1_2 = sum(S1_2),
    S2_m1 = sum(S2_m1),
    S2_0 = sum(S2_0),
    S2_1 = sum(S2_1),
    S2_2 = sum(S2_2)
  ) %>% select(lakeID, variable, base)


#IDEE: add line with mean change per depth and in total

FigAll<-all_diff_presabs_tobase %>% # filter(S1minusBase!=0)%>%filter(S2minusBase!=0)%>%
  gather("scenario", "PreAbsChange", c(16:32)) %>% # 4,
  group_by(lakeID, variable, scenario) %>%
  count(PreAbsChange) %>%
  filter(PreAbsChange != 0) %>%
  left_join(Nspec_base_perdepth, by=c("lakeID"="lakeID","variable"="variable")) %>%
  ungroup() %>%
  mutate(nPerc = (n/base)*100) %>%
  add_row(scenario = "base", variable = c(-5.0)) %>%

  mutate(scenarioTemp = 
           ifelse(scenario=="S0_m1minusBase" | 
                    scenario=="S0_1minusBase" |  
                    scenario=="S0_2minusBase" | scenario=="base","Temp_0",
           ifelse(scenario=="S1_m1minusBase" | scenario=="S1_1minusBase" | 
                    scenario=="S1_2minusBase" | scenario=="S1_0minusBase","Temp_1",
            ifelse(scenario=="S2_m1minusBase" | scenario=="S2_1minusBase" | 
                     scenario=="S2_2minusBase" | scenario=="S2_0minusBase",
                   "Temp_2","others"))
                                )) %>%
    mutate(scenarioTurbNut = 
           ifelse(scenario=="S0_m1minusBase" | 
                    scenario=="S1_m1minusBase" |  
                    scenario=="S2_m1minusBase" ,"TurbNutr_m1",
           ifelse(scenario=="base" | scenario=="S1_0minusBase" | 
                    scenario=="S2_0minusBase" ,"TurbNutr_0",
            ifelse(scenario=="S0_1minusBase" | scenario=="S1_1minusBase" | 
                     scenario=="S2_1minusBase" ,
                   "TurbNutr_1",
                   ifelse(scenario=="S0_2minusBase" | scenario=="S1_2minusBase" | 
                     scenario=="S2_2minusBase" ,
                   "TurbNutr_2","others"))
                                ))) %>%
    transform(scenarioTurbNut = factor(
    scenarioTurbNut,
    levels = c(
      "TurbNutr_m1",
      "TurbNutr_0",
      "TurbNutr_1",
      "TurbNutr_2"
    )
  )) %>%
  
  filter(scenarioTemp!="NA") %>%
  filter(scenarioTurbNut!="NA") %>%
  ggplot(aes(
    x = factor(variable),
    y = n,
    fill = factor(PreAbsChange)
  )) +
  facet_grid( scenarioTemp~scenarioTurbNut,
              labeller = labeller(scenarioTurbNut = scen.labs.Turb)
              #nrow = 3
              ) +
  geom_boxplot(aes()) +
  ylab("species")+
  scale_x_discrete(limits = rev) +
  guides(fill = guide_legend(title = "Change")) +
  scale_fill_manual(labels = c("looser", "winner"), #,"others","TempEffect","TurbNutrEffect"
                    values = (WinnerLoserPalette))+ #,"white","mistyrose","cornsilk"
  ggtitle(expression(decreasing %<-% Turbidity/Nutrients %->% increasing))+ 
  theme(plot.title = element_text(size = 10,color = "grey50"))+
  theme(legend.position = "bottom")+
  scale_y_continuous(
    sec.axis = dup_axis(name = expression(Temperature %->% increasing), breaks = NULL))+ 
  theme(axis.title.y.right = element_text(size=10,color = "grey50"))+
  xlab("Depth") +
  ylab("Species number change")


FigTurbNutr <- scenTurbNutr_diff_presabs_toZero %>% 
    gather("scenario", "PreAbsChange", c(13:29)) %>% # 4,
  group_by(lakeID, variable, scenario) %>%
  count(PreAbsChange) %>%
  filter(PreAbsChange != 0)%>%
  ungroup() %>%
  add_row(scenario = "S2_0", variable = c(-5.0)) %>%
  #add_row(scenario = "blank1", variable = c(-5.0)) %>%
  #add_row(scenario = "blank2", variable = c(-5.0)) %>%
  #add_row(scenario = "blank3", variable = c(-5.0)) %>%

  mutate(scenarioTurb = 
           ifelse(scenario=="S2_Nm1_T0minusS2_0" | scenario=="S2_0" |
                    scenario=="S2_N1_T0minusS2_0","Turb_0",
                         ifelse(scenario=="S2_m1minusS2_0" | scenario=="S2_N0_Tm1minusS2_0" |
                                  scenario=="S2_N1_Tm1minusS2_0","Turb_m1",
                                ifelse(scenario=="S2_Nm1_T1minusS2_0" |
                                         scenario=="S2_N0_T1minusS2_0" |
                                         scenario=="S2_1minusS2_0","Turb_1","others"))
                                )) %>%
    transform(scenarioTurb = factor(
  scenarioTurb,
    levels = c(
      "Turb_m1", "Turb_0","Turb_1"
      )
  ))  %>%
    mutate(scenarioNutr = 
           ifelse(scenario=="S2_m1minusS2_0" | scenario=="S2_Nm1_T0minusS2_0" |
                    scenario=="S2_Nm1_T1minusS2_0","Nutr_m1",
                         ifelse(scenario=="S2_N0_Tm1minusS2_0" | scenario=="S2_0" |
                                  scenario=="S2_N0_T1minusS2_0","Nutr_0",
                                ifelse(scenario=="S2_N1_Tm1minusS2_0" |
                                         scenario=="S2_N1_T0minusS2_0" |
                                         scenario=="S2_1minusS2_0","Nutr_1","others"))
                                )) %>%
  transform(scenarioNutr = factor(
  scenarioNutr,
    levels = c(
      "Nutr_m1", "Nutr_0","Nutr_1"
      )
  ))  %>%
  filter(scenarioNutr!="NA") %>%
  filter(scenarioTurb!="NA") %>%
  ggplot(aes(x = factor(variable), y = n, fill = factor(PreAbsChange))) +
  geom_boxplot(aes()) +
  ylab("species") +
  facet_grid(scenarioTurb~scenarioNutr #, nrow = 3,labeller = labeller(scenario = scen2.labs)
             ) +
  scale_x_discrete(limits = rev) +
  xlab("Depth") +
  ylab("Species mumber change") + ylim(0,40) +
  guides(fill = guide_legend(title = "Change")) +
  scale_y_continuous(
    sec.axis = dup_axis(name = expression(decreasing %<-% Turbidity %->% increasing), 
                        breaks = NULL))+ 
  theme(axis.title.y.right = element_text(size=10,color = "grey50"))+
    ggtitle(expression(decreasing %<-% Nutrients %->% increasing))+ 
  theme(plot.title = element_text(size = 10,color = "grey50"))+
  scale_fill_manual(labels = c("looser", "winner"), 
                               values = (WinnerLoserPalette))+
  theme(legend.position = "bottom")


FIG3<-FigAll / (FigTurbNutr+plot_spacer()+ 
  plot_layout(widths = c(3, 1)))  & theme(legend.position = "bottom")
FIG3+ 
  plot_annotation(tag_levels = 'A') + 
  plot_layout(guides = "collect")

```




## Q3 - Traits Winner / Loser


### S2_m1 and S2_1
```{r}
# WinnerLoserTraitsS2_1_S2_m1_all<-all_diff_presabs_tobase %>% 
#   #mutate(Trophie = ifelse(speciesID %in% c(14001:14300), "oligo",
#   #                        ifelse(speciesID %in% c(15001:15300), "meso",
#   #                               ifelse(speciesID %in% c(16001:16300), "eu",NA)))) %>%
#   select(speciesID,lakeID, variable,base,
#          S2_1,S2_m1) %>%
#   group_by(speciesID, lakeID) %>% #to make it independent from depth
#   summarise(S2_1=sum(S2_1),
#             S2_m1=sum(S2_m1),
#             base=sum(base)) %>%
#   mutate(S2_1=ifelse(S2_1>0,1,0),
#          S2_m1=ifelse(S2_m1>0,1,0),
#          base=ifelse(base>0,1,0)) %>%
#   mutate(S2_1minusBase=S2_1 - base,
#          S2_m1minusBase=S2_m1 - base) %>%
#   ungroup() %>%
#   
#   group_by(speciesID) %>%
#   summarise(lakeWinLostS2_1 = sum(S2_1minusBase),
#             lakeWinLostS2_m1 = sum(S2_m1minusBase)) %>%
#     mutate(lakeWinLostS2_1=ifelse(lakeWinLostS2_1>0,1,
#                             ifelse(lakeWinLostS2_1<0,-1,0)),
#            lakeWinLostS2_m1=ifelse(lakeWinLostS2_m1>0,1,
#                             ifelse(lakeWinLostS2_m1<0,-1,0))) %>%
#   left_join(data_spec_para, by=c("speciesID"="specNr")) %>%
#   #gather("parameter","value",c(5,7:24)) %>%
#   select(-tuberEndAge, -Group)%>%
#   gather("Scenario","WinLost",2:3) 
# 
# 
# data.glmS2_1  <- WinnerLoserTraitsS2_1_S2_m1_all %>% 
#   filter(Scenario=="lakeWinLostS2_1") %>%
#   filter(WinLost!=0) %>%
#   mutate(WinLost=factor(WinLost)) %>%
#   select(-speciesID,-Scenario) %>%
#   #spread(parameter,value)%>%
#   ungroup() %>%
#   as.data.frame() %>%
#   mutate_at(vars(-Species,-WinLost), normalize, method="range",range = c(0, 1))
# 
# modSpaceS2_1 <- glm(formula = factor(WinLost)~ . ,data=data.glmS2_1[,-c(1)], family = binomial())
# 
# #summary(modSpaceS2_1)
# glmSpace2_1 <- drop1(modSpaceS2_1, test="Chisq")
# 
# #glmSpace2_1
# 
# #tab_model(modSpace)
# 
# T2_1<-plot_model(modSpaceS2_1, show.values = TRUE, 
#            value.offset = .3, digits=1,sort.est = F,
#            title = "S2_1: Losers - Winners",
#            rm.terms = c("germinationDay", "heightMax", "hPhotoTemp","maxAge","pPhotoTemp",
#                         "rootShootRatio","seedBiomass","seedsEndAge","seedsStartAge")) #, 
# 
# # other szenario
# data.glmS2_m1  <- WinnerLoserTraitsS2_1_S2_m1_all %>% 
#   filter(Scenario=="lakeWinLostS2_m1") %>%
#   filter(WinLost!=0) %>%
#   mutate(WinLost=factor(WinLost)) %>%
#   select(-speciesID,-Scenario) %>%
#   #spread(parameter,value)%>%
#   ungroup() %>%
#   as.data.frame() %>%
#   mutate_at(vars(-Species,-WinLost), normalize, method="range",range = c(0, 1))
# 
# modSpaceS2_m1 <- glm(formula = factor(WinLost)~ . ,data=data.glmS2_m1[,-c(1)], family = binomial())
# 
# #summary(modSpaceS2_m1)
# glmSpace2_m1 <- drop1(modSpaceS2_m1, test="Chisq")
# 
# #glmSpace2_m1
# 
# #tab_model(modSpace)
# 
# T2_m1<-plot_model(modSpaceS2_m1, show.values = TRUE, 
#            value.offset = .3, digits=1,sort.est = F,
#            title = "Traits of Losers - Winners",
#            rm.terms = c("germinationDay", "heightMax", "hPhotoTemp","maxAge","pPhotoTemp",
#                         "rootShootRatio","seedBiomass","seedsEndAge","seedsStartAge")) #, 
# 
# (T2_m1+
#     labs(subtitle = "A - S2_m1")) + (T2_1+
#   theme(axis.title.y=element_blank(),
#         axis.text.y=element_blank(),
#         axis.ticks.y=element_blank())+
#     labs(subtitle = "B - S2_1", title="")) #+ plot_annotation(tag_levels = 'A')
```


### S0_m1 and S0_1

#### ALL (FIG4)

```{r}
WinnerLoserTraitsS0_1_S0_m1_all<-all_diff_presabs_tobase %>% 
  #filter(variable=="-3" | variable=="-5")%>%
  select(speciesID,lakeID, variable,base, S0_1,S0_m1) %>%
  group_by(speciesID, lakeID) %>% #to make it independent from depth
  summarise(S0_1=sum(S0_1),
            S0_m1=sum(S0_m1),
            base=sum(base)) %>%
  mutate(S0_1=ifelse(S0_1>0,1,0),
         S0_m1=ifelse(S0_m1>0,1,0),
         base=ifelse(base>0,1,0)) %>%
  mutate(S0_1minusBase=S0_1 - base,
         S0_m1minusBase=S0_m1 - base) %>%
  ungroup() %>%
  
  group_by(speciesID) %>%
  summarise(lakeWinLostS0_1 = sum(S0_1minusBase),
            lakeWinLostS0_m1 = sum(S0_m1minusBase)) %>%
  mutate(lakeWinLostS0_1=ifelse(lakeWinLostS0_1>0,1,
                            ifelse(lakeWinLostS0_1<0,-1,0)),
           lakeWinLostS0_m1=ifelse(lakeWinLostS0_m1>0,1,
                            ifelse(lakeWinLostS0_m1<0,-1,0))) %>%
  left_join(data_spec_para, by=c("speciesID"="specNr")) %>%
  select(-tuberEndAge, -Group)%>%
  gather("Scenario","WinLost",2:3) 


data.glmS0_1  <- WinnerLoserTraitsS0_1_S0_m1_all %>% 
  filter(Scenario=="lakeWinLostS0_1") %>%
  filter(WinLost!=0) %>%
  mutate(WinLost=factor(WinLost)) %>%
  select(-speciesID,-Scenario) %>%
  ungroup() %>%
  as.data.frame() %>%
  mutate_at(vars(-Species,-WinLost), normalize, method="range",range = c(0, 1))

modSpaceS0_1 <- glm(formula = factor(WinLost)~ . ,data=data.glmS0_1[,-c(1)], family = binomial())

summary(modSpaceS0_1)
glmSpace0_1 <- drop1(modSpaceS0_1, test="Chisq")

glmSpace0_1




# other szenario S0_m1
data.glmS0_m1  <- WinnerLoserTraitsS0_1_S0_m1_all %>% 
  filter(Scenario=="lakeWinLostS0_m1") %>%
  filter(WinLost!=0) %>%
  mutate(WinLost=factor(WinLost)) %>%
  select(-speciesID,-Scenario) %>%
  #spread(parameter,value)%>%
  ungroup() %>%
  as.data.frame() %>%
  mutate_at(vars(-Species,-WinLost), normalize, method="range",range = c(0, 1))

modSpaceS0_m1 <- glm(formula = factor(WinLost)~ . , 
                     data=data.glmS0_m1[,-c(1)], family = binomial())


summary(modSpaceS0_m1)
glmSpace0_m1 <- drop1(modSpaceS0_m1, test="Chisq")

glmSpace0_m1

#tab_model(modSpace)

## Select relevant (siginificant) parameters
toselect.S0_m1 <- summary(modSpaceS0_m1)$coeff[-1,4] < 0.05
relevant.S0_m1 <- names(toselect.S0_m1)[toselect.S0_m1 == TRUE] 

toselect.S0_1 <- summary(modSpaceS0_1)$coeff[-1,4] < 0.05
relevant.S0_1 <- names(toselect.S0_1)[toselect.S0_1 == TRUE] 

relevant <- c(relevant.S0_1,relevant.S0_m1) %>% unique()

T0_m1_all<-plot_model(modSpaceS0_m1, show.values = TRUE, 
           value.offset = .3, digits=1,sort.est = F,
           title = "",
           terms=relevant) #, 

T0_1_all<-plot_model(modSpaceS0_1, show.values = TRUE, 
           value.offset = .3, digits=1,sort.est = F,
           #title = "S0_1: Losers - Winners",
           terms = relevant) #,


Fig4fin<-(T0_m1_all+
    labs(subtitle = "(a) Decreased turbidity \nand nutrients (-25%)") + labs(x="Species trait")) + (T0_1_all+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
    labs(subtitle = "(b) Increased turbidity \nand nutrients (25%)", title="")) #+ plot_annotation(tag_levels = 'A')

Fig4fin

#ggsave("Fig4.png", Fig4fin, width = 6.5, height=4, dpi="print", bg="white")
```



#### S0_1
```{r, fig.width=4, fig.height=5}

data.glmS0_1  <- WinnerLoserTraitsS0_1_S0_m1_all %>% 
  filter(Scenario=="lakeWinLostS0_1") %>%
  filter(WinLost!=0) %>%
  mutate(WinLost=factor(WinLost)) %>%
  select(-speciesID,-Scenario) %>%
  ungroup() %>%
  as.data.frame() %>%
  mutate_at(vars(-Species,-WinLost), normalize, method="range",range = c(0, 1))

modSpaceS0_1 <- glm(formula = factor(WinLost)~ . ,data=data.glmS0_1[,-c(1)], family = binomial())
toselect.S0_1 <- summary(modSpaceS0_1)$coeff[-1,4] < 0.05
relevant.S0_1 <- names(toselect.S0_1)[toselect.S0_1 == TRUE] 

relevant <- c(relevant.S0_1) %>% unique()



T0_1_all<-plot_model(modSpaceS0_1, show.values = TRUE, 
           value.offset = .3, digits=1,sort.est = F,
           title = "S0_1: Losers - Winners",
           terms = relevant, vline.color = "red") #,


(T0_1_all+
    labs(subtitle = "A - S0_m1")) #+ plot_annotation(tag_levels = 'A')
```




How good are the GLMs
```{r}
# with(summary(modSpaceS0_1), 1 - deviance/null.deviance)
# with(summary(modSpaceS0_m1), 1 - deviance/null.deviance)
# 
# 
# library(ResourceSelection)
# hoslem.test(modSpaceS0_1$y, modSpaceS0_1$fitted)
# hoslem.test(modSpaceS0_m1$y, modSpaceS0_m1$fitted)

#https://easystats.github.io/performance/articles/r2.html 
performance::r2(modSpaceS0_1)
performance::r2(modSpaceS0_m1)

```
In the context of a generalized linear model (e.g., a logistic model which outcome is binary), R2 doesn’t measure the percentage of “explained variance”, as this concept doesn’t apply. However, the R2s that have been adapted for GLMs have retained the name of “R2”, mostly because of the similar properties (the range, the sensitivity, and the interpretation as the amount of explanatory power).

Number of Winners / Loser in both scenarios
```{r}
NWinnerLoserS0_1<-data.glmS0_1 %>% 
  count(WinLost) %>% 
  mutate(S0_1_P=(n/NSPECbase*100))%>% select(-n)
NWinnerLoserS0_m1<- data.glmS0_m1 %>% count(WinLost)%>%
  mutate(S0_m1_P=(n/NSPECbase*100))%>% select(-n)

NWinnerLoserS0_1 %>% left_join(NWinnerLoserS0_m1, by="WinLost")
```






#### DEEP depth 
```{r}
WinnerLoserTraitsS0_1_S0_m1_dd<-all_diff_presabs_tobase %>% 
  filter(variable=="-3" | variable=="-5")%>%
  select(speciesID,lakeID, variable,base, S0_1,S0_m1) %>%
  group_by(speciesID, lakeID) %>% #to make it independent from depth
  summarise(S0_1=sum(S0_1),
            S0_m1=sum(S0_m1),
            base=sum(base)) %>%
  mutate(S0_1=ifelse(S0_1>0,1,0),
         S0_m1=ifelse(S0_m1>0,1,0),
         base=ifelse(base>0,1,0)) %>%
  mutate(S0_1minusBase=S0_1 - base,
         S0_m1minusBase=S0_m1 - base) %>%
  ungroup() %>%
  
  group_by(speciesID) %>%
  summarise(lakeWinLostS0_1 = sum(S0_1minusBase),
            lakeWinLostS0_m1 = sum(S0_m1minusBase)) %>%
  mutate(lakeWinLostS0_1=ifelse(lakeWinLostS0_1>0,1,
                            ifelse(lakeWinLostS0_1<0,-1,0)),
           lakeWinLostS0_m1=ifelse(lakeWinLostS0_m1>0,1,
                            ifelse(lakeWinLostS0_m1<0,-1,0))) %>%
  left_join(data_spec_para, by=c("speciesID"="specNr")) %>%
  select(-tuberEndAge, -Group)%>%
  gather("Scenario","WinLost",2:3) 


data.glmS0_1_deep  <- WinnerLoserTraitsS0_1_S0_m1_dd %>% 
  filter(Scenario=="lakeWinLostS0_1") %>%
  filter(WinLost!=0) %>%
  mutate(WinLost=factor(WinLost)) %>%
  select(-speciesID,-Scenario) %>%
  ungroup() %>%
  as.data.frame() %>%
  mutate_at(vars(-Species,-WinLost), normalize, method="range",range = c(0, 1))

modSpaceS0_1_deep <- glm(formula = factor(WinLost)~ . ,data=data.glmS0_1_deep[,-c(1)], family = binomial())

#summary(modSpaceS2_1)
glmSpace0_1 <- drop1(modSpaceS0_1_deep, test="Chisq")

#glmSpace2_1

# other szenario
data.glmS0_m1_deep  <- WinnerLoserTraitsS0_1_S0_m1_dd %>% 
  filter(Scenario=="lakeWinLostS0_m1") %>%
  filter(WinLost!=0) %>%
  mutate(WinLost=factor(WinLost)) %>%
  select(-speciesID,-Scenario) %>%
  #spread(parameter,value)%>%
  ungroup() %>%
  as.data.frame() %>%
  mutate_at(vars(-Species,-WinLost), normalize, method="range",range = c(0, 1))

modSpaceS0_m1 <- glm(formula = factor(WinLost)~ . , 
                     data=data.glmS0_m1_deep[,-c(1)], family = binomial())


#summary(modSpaceS2_m1)
glmSpace0_m1 <- drop1(modSpaceS0_m1, test="Chisq")

#glmSpace2_m1

#tab_model(modSpace)

## Select relevant (siginificant) parameters
toselect.S0_m1 <- summary(modSpaceS0_m1)$coeff[-1,4] < 0.05
relevant.S0_m1 <- names(toselect.S0_m1)[toselect.S0_m1 == TRUE] 

toselect.S0_1 <- summary(modSpaceS0_1)$coeff[-1,4] < 0.05
relevant.S0_1 <- names(toselect.S0_1)[toselect.S0_1 == TRUE] 

relevant <- c(relevant.S0_1,relevant.S0_m1) %>% unique()

T0_m1_d<-plot_model(modSpaceS0_m1, show.values = TRUE, 
           value.offset = .3, digits=1,sort.est = F,
           title = "Traits of Losers - Winners",
           terms=relevant) #, 

T0_1_d<-plot_model(modSpaceS0_1, show.values = TRUE, 
           value.offset = .3, digits=1,sort.est = F,
           title = "S0_1: Losers - Winners",
           terms = relevant) #,


(T0_m1_d+
    labs(subtitle = "A - S0_m1")) + (T0_1_d+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
    labs(subtitle = "B - S0_1", title="")) #+ plot_annotation(tag_levels = 'A')
```


#### SHALLOW depth

```{r}
WinnerLoserTraitsS0_1_S0_m1_ddd<-all_diff_presabs_tobase %>% 
  filter(variable=="-1.5" | variable=="-0.5")%>%
  select(speciesID,lakeID, variable,base, S0_1,S0_m1) %>%
  group_by(speciesID, lakeID) %>% #to make it independent from depth
  summarise(S0_1=sum(S0_1),
            S0_m1=sum(S0_m1),
            base=sum(base)) %>%
  mutate(S0_1=ifelse(S0_1>0,1,0),
         S0_m1=ifelse(S0_m1>0,1,0),
         base=ifelse(base>0,1,0)) %>%
  mutate(S0_1minusBase=S0_1 - base,
         S0_m1minusBase=S0_m1 - base) %>%
  ungroup() %>%
  
  group_by(speciesID) %>%
  summarise(lakeWinLostS0_1 = sum(S0_1minusBase),
            lakeWinLostS0_m1 = sum(S0_m1minusBase)) %>%
  mutate(lakeWinLostS0_1=ifelse(lakeWinLostS0_1>0,1,
                            ifelse(lakeWinLostS0_1<0,-1,0)),
           lakeWinLostS0_m1=ifelse(lakeWinLostS0_m1>0,1,
                            ifelse(lakeWinLostS0_m1<0,-1,0))) %>%
  left_join(data_spec_para, by=c("speciesID"="specNr")) %>%
  select(-tuberEndAge, -Group)%>%
  gather("Scenario","WinLost",2:3) 


data.glmS0_1_shallow  <- WinnerLoserTraitsS0_1_S0_m1_ddd %>% 
  filter(Scenario=="lakeWinLostS0_1") %>%
  filter(WinLost!=0) %>%
  mutate(WinLost=factor(WinLost)) %>%
  select(-speciesID,-Scenario) %>%
  ungroup() %>%
  as.data.frame() %>%
  mutate_at(vars(-Species,-WinLost), normalize, method="range",range = c(0, 1))

modSpaceS0_1 <- glm(formula = factor(WinLost)~ . ,data=data.glmS0_1_shallow[,-c(1)], family = binomial())

#summary(modSpaceS2_1)
glmSpace0_1 <- drop1(modSpaceS0_1, test="Chisq")

#glmSpace2_1

#tab_model(modSpace)

# Will be ploted later
# T0_1<-plot_model(modSpaceS0_1, show.values = TRUE, 
#            value.offset = .3, digits=1,sort.est = F,
#            title = "S0_1: Losers - Winners"#,
#            #rm.terms = c("germinationDay", "heightMax", "hPhotoTemp","maxAge","pPhotoTemp",
#           #              "rootShootRatio","seedBiomass","seedsEndAge","seedsStartAge")
#            ) #, 

# other szenario
data.glmS0_m1_shallow  <- WinnerLoserTraitsS0_1_S0_m1_ddd %>% 
  filter(Scenario=="lakeWinLostS0_m1") %>%
  filter(WinLost!=0) %>%
  mutate(WinLost=factor(WinLost)) %>%
  select(-speciesID,-Scenario) %>%
  #spread(parameter,value)%>%
  ungroup() %>%
  as.data.frame() %>%
  mutate_at(vars(-Species,-WinLost), normalize, method="range",range = c(0, 1))

modSpaceS0_m1 <- glm(formula = factor(WinLost)~ . , 
                     data=data.glmS0_m1_shallow[,-c(1)], family = binomial())


#summary(modSpaceS2_m1)
glmSpace0_m1 <- drop1(modSpaceS0_m1, test="Chisq")

#glmSpace2_m1

#tab_model(modSpace)

## Select relevant (siginificant) parameters
toselect.S0_m1 <- summary(modSpaceS0_m1)$coeff[-1,4] < 0.05
relevant.S0_m1 <- names(toselect.S0_m1)[toselect.S0_m1 == TRUE] 

toselect.S0_1 <- summary(modSpaceS0_1)$coeff[-1,4] < 0.05
relevant.S0_1 <- names(toselect.S0_1)[toselect.S0_1 == TRUE] 

relevant <- c(relevant.S0_1,relevant.S0_m1) %>% unique()

T0_m1_s<-plot_model(modSpaceS0_m1, show.values = TRUE, 
           value.offset = .3, digits=1,sort.est = F,
           title = "Traits of Losers - Winners",
           terms=relevant) #, 

T0_1_s<-plot_model(modSpaceS0_1, show.values = TRUE, 
           value.offset = .3, digits=1,sort.est = F,
           title = "S0_1: Losers - Winners",
           terms = relevant) #,


(T0_m1_s+
    labs(subtitle = "A - S0_m1")) + (T0_1_s+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
    labs(subtitle = "B - S0_1", title="")) #+ plot_annotation(tag_levels = 'A')
```


#### Deep and Shallow and All
```{r, fig.height=8, fig.width=5}
# ((T0_m1_s+
#     labs(subtitle = "A - S0_m1 shallow")) + 
#   (T0_1_s+
#   theme(axis.title.y=element_blank(),
#         axis.text.y=element_blank(),
#         axis.ticks.y=element_blank())+
#     labs(subtitle = "B - S0_1 shallow", title=""))) /
#   ((T0_m1_d+
#     labs(subtitle = "C - S0_m1 deep", title="")) + (T0_1_d+
#   theme(axis.title.y=element_blank(),
#         axis.text.y=element_blank(),
#         axis.ticks.y=element_blank()))+
#     labs(subtitle = "D - S0_1 deep", title=""))/
#   ((T0_m1_all+
#     labs(subtitle = "E - S0_m1 all depth", title="")) + (T0_1_all+
#   theme(axis.title.y=element_blank(),
#         axis.text.y=element_blank(),
#         axis.ticks.y=element_blank()))+
#     labs(subtitle = "F - S0_1 all depth", title=""))
```

#### Winner/Loser 
```{r}
# tw1<-data.glmS0_m1_deep %>% count(WinLost) %>%
#   mutate(S0_m1_deep_P=(n/NSPECbase*100))%>% select(-n)
# 
# tw2<-data.glmS0_1_deep %>% count(WinLost) %>%
#   mutate(S0_1_deep_P=(n/NSPECbase*100))%>% select(-n)
# 
# tw3<-data.glmS0_m1_shallow %>% count(WinLost) %>%
#   mutate(S0_m1_sha_P=(n/NSPECbase*100))%>% select(-n)
# 
# tw4<-data.glmS0_1_shallow %>% count(WinLost) %>%
#   mutate(S0_1_sha_P=(n/NSPECbase*100))%>% select(-n)
# 
# tw1 %>% left_join(tw2, by="WinLost")%>% left_join(tw3, by="WinLost")%>% 
#   left_join(tw4, by="WinLost")
```





### S2_0
```{r}
WinnerLoserTraitsS2_0<-all_diff_presabs_tobase %>% 
  #filter(variable=="-3" | variable=="-5")%>%
  select(speciesID,lakeID, variable,base, S2_0) %>%
  group_by(speciesID, lakeID) %>% #to make it independent from depth
  summarise(S2_0=sum(S2_0),
            base=sum(base)) %>%
  mutate(S2_0=ifelse(S2_0>0,1,0),
         base=ifelse(base>0,1,0)) %>%
  mutate(S2_0minusBase=S2_0 - base) %>%
  ungroup() %>%
  
  group_by(speciesID) %>%
  summarise(lakeWinLostS2_0 = sum(S2_0minusBase)) %>%
  mutate(lakeWinLostS2_0=ifelse(lakeWinLostS2_0>0,1,
                            ifelse(lakeWinLostS2_0<0,-1,0))) %>%
  left_join(data_spec_para, by=c("speciesID"="specNr")) %>%
  select(-tuberEndAge, -Group)


data.glmS2_0  <- WinnerLoserTraitsS2_0 %>% 
  #filter(lakeWinLostS2_0!=0) %>%
  mutate(lakeWinLostS2_0=factor(lakeWinLostS2_0)) %>%
  select(-speciesID) %>%
  ungroup() %>%
  as.data.frame() %>%
  mutate_at(vars(-Species,-lakeWinLostS2_0), normalize, method="range",range = c(0, 1))

modSpaceS2_0 <- glm(formula = factor(lakeWinLostS2_0)~ . ,
                    data=data.glmS2_0[,-2], family = binomial())

#summary(modSpaceS2_0)
glmSpace2_0 <- drop1(modSpaceS2_0, test="Chisq")

#glmSpace2_0



## Select relevant (siginificant) parameters
toselect.S2_0 <- summary(modSpaceS2_0)$coeff[-1,4] < 0.05
relevant.S2_0 <- names(toselect.S2_0)[toselect.S2_0 == TRUE] 

relevant <- c(relevant.S0_1,relevant.S0_m1,relevant.S0_m1) %>% unique()


T2_0_all<-plot_model(modSpaceS2_0, show.values = TRUE, 
           value.offset = .3, digits=1,sort.est = F,
           title = "Traits of Losers - Winners",
           terms=relevant) #, 

T0_m1_all<-plot_model(modSpaceS0_m1, show.values = TRUE, 
           value.offset = .3, digits=1,sort.est = F,
           title = "Traits of Losers - Winners",
           terms=relevant) #, 

T0_1_all<-plot_model(modSpaceS0_1, show.values = TRUE, 
           value.offset = .3, digits=1,sort.est = F,
           title = "S0_1: Losers - Winners",
           terms = relevant) #,


(T0_m1_all+
    labs(subtitle = "A - T&N decrease")) + (T0_1_all+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
    labs(subtitle = "B - T&N increase", title=""))+
  (T2_0_all+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
    labs(subtitle = "C - Temp. increase", title=""))
```


